\documentclass{article}
\title{Personal Statement}
\author{Tianming Lu}
\begin{document}
\maketitle
\paragraph{start}
Before entering into univerity,since I had limited access to computer and internet, I did not have high programming skills and the only programming language I knew was VB. At first, I choose software engineering bacuase I thought it's cool and I could easily find a job after graduation. But after I started my study in the university, I began to feel the real charm of software engineering and really love it. I have known that I learn the major not because it can help me find a job easily, but becuase I just want to learn. I was curious about various topic in the field of my major, such as design pattern, functional programming, intellegent system and so on.
Later, I found that *** is specially attractive to me. I am not satisfied with the knowledge I learnt from class, thus I start to learn by myself. And I knew, to better understand the knowledge, I need to further my education 
\paragraph{}
why software engineering, computer science
\paragraph{why this subject(ML)}
I find machind learning especielly attractive to me. With machine learning, the function of software is highly extended. Software can do thing it can not do before. For example, we can predict people's behavior and make decission based upon the prediction. What's more, it is the era of data now. The more infornmation you dig from the data, the more advantage you will have. And machine learning play a important role in this era. Without machine learning, those data would be useless. 
\paragraph{personal characters}

\paragraph{achievements}
\paragraph{future goals} 
\paragraph{personal experience 1}
last year, I got the chance to take part in a seminar for graduates. It is about Kinect and depth image. In the seminar, we read papers, made presentations and discuessed freely. And it's also in this seminar, we planed to implement a Kinect teaching assistant system by which teacher can teach in a more effiecient way. And my job was to implement the gesture recognition module. As I did not have much knowledge related to the project, I need to learn these knowledge from scrath by myself. I googled the topic, read several papers, compared different technologies and finally finished the job successfully. This seminar helped me improve various abilities including searching infornmation, reader papers and so on. And I enjoy the process of discovering and learning new things.   
\paragraph{personal experience 2}
In this summer, after fierce competition, I become an intern of Microsoft, Shanghai, China. I believe this is an affirmation of my ability and hardwork in university.  
\paragraph{for French}
I know that engineers are highly respected in French and French has the greatest engineer cultivation system. Thus why I want to go to French to further my engineering education.
\end{document}