\documentclass[a4paper]{article}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancypagestyle{mystyle}{%
  \fancyhf{}
  \lfoot{\small Tianming Lu}
  \cfoot{\small \today}
  \rfoot{\small \thepage}
  \renewcommand{\headrulewidth}{0pt}
}
\pagestyle{mystyle}

\title{Statement of Purpose}
\author{Tianming Lu \\
		Software Institute, Nanjing University\\
		lutianming1005@gmail.com}
\date{}
\begin{document}
\maketitle\thispagestyle{mystyle}
\paragraph{}
About one year ago, I read a post about the free online courses, which is known as Coursera today. The machine learning class taught by Professor Andrew Ng attracted me and I signed in. In the class, there was a programming assignment that asked us to recognize handwritten digits. At the same time, I was taking a course introducing multimedia and image in my institute. Solving image problems with machine learning techniques amazed me and I found it really interesting. Thus I began to narrow my interests down to image process and machine learning.
\paragraph{}
I know that French engineer education is rather efficient for training an elite in engineering. Students not only learn in class, but also learn in company. The theory and practice are highly combined with each other, which is proved to be an efficient way to teach and learn. Thus, being a student whose major is engineering, I believe France is the right place to further my education. And ParisTech, with each school recognized as the best in its domain in France, is the first choice for me. Especially, I find that Telecom ParisTech attracts me the most because of the Signal \& Image Process Department within it. The curriculum provided by the TSI department includes image, multimedia, machine learning and so on. These courses can meet my personal interests and professional goals perfectly.
\paragraph{}
In the first two years of university study, I have gained lots of essential knowledge in math and software engineering. This is the base of my future career. In the second grade, We had a statistics course. In this course, we have some programming assignments. Many students chose Java, which they were most familiar with, to do the assignments. But I chose R, a new language I never used before, because our professor mentioned in class that R is the language designed for statistical computing. Though I need to learn a new programming language from scratch, I really enjoy the process. And happily, I got a score of 98 in this course finally.
\paragraph{}
My professional goals are extremely clear. I plan to be a software engineer in the field of image processing or machine learning. To reach my goal, I asked to participate in the Seminar of Kinect and Depth Image when I was in third grade. The seminar was hold for graduate students in my institute. In the seminar, we read papers, made presentations and did research project. I also implemented a simple gesture recognition system based on Kinect. It was full of fun. I found there are four research groups in the STI department, Telecom ParisTech. They all organize many interesting seminars. For example, The STA group holds a seminar called Statistical Machine Learning in Paris. Besides the curriculum, these seminars would be great resource for me to learn advanced technology that is useful for my future career. 
\paragraph{}
What's more, I would like to be a kind of engineer that can help people solve real problems and make their life better. During my internship in Microsoft, China, I built a tool to help developers finish job faster and easier. This tool can help them save lots of time. When I see my job can help others, I feel a great sense of accomplishment(I attached the internship performance assessment after this statement for reference). In Nanjing, there is a startup that develops smartphone OS designed for blind people. One thing they want to do now is to use the smartphone camera to recognize the value of paper money because it is sometimes difficult for blind people to touch and feel the value of old money. This is very meaningful and can help many blind people. And I plan to try to implement it as my graduation project. Meaningful project like that is also what I want to do in the future as an engineer.
\paragraph{}   
During the past three years of study, I have built a strong base for my future career. But that is still not enough for me and I want to be more professional. The curriculum provided by the TSI department in Telecom ParisTech provides a perfect combination of image process and machine learning. All these will help me become more professional in the fields. And I will be well prepared for the future challenge.
\end{document}